---
title: "CARPS Reproducibility Report"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r}
articleID <- "3-9-2014_PS" # insert the article ID code here e.g., "10-3-2015_PS"
reportType <- 'pilot'
pilotNames <- "Katherine Hermann, Benjamin deMayo" # insert the pilot's name here e.g., "Tom Hardwicke". If there are multiple pilots enter both names in a character string e.g., "Tom Hardwicke, Bob Dylan"
copilotNames <- "Emily Hembacher" # insert the co-pilot's name here e.g., "Michael Frank". If there are multiple co-pilots enter both names in a character string e.g., "Tom Hardwicke, Bob Dylan"
pilotTTC <- 240 # insert the pilot's estimated time to complete (in minutes, fine to approximate) e.g., 120
copilotTTC <- NA # insert the co- pilot's estimated time to complete (in minutes, fine to approximate) e.g., 120
pilotStartDate <- as.Date("11/04/17", format = "%m/%d/%y") # insert the pilot's start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- as.Date("06/13/18", format = "%m/%d/%y") # insert the co-pilot's start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- as.Date("", format = "%m/%d/%y") # copilot insert the date of final report completion (after any necessary rounds of author assistance) in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

-------

#### Methods summary: 
This analysis pertains to Experiment 2 of de la Fuente et al. (2014). In that experiment, the researchers tested the question of whether temporal focus differs between Moroccan and Spanish cultures, hypothesizing that Moroccans are more past-focused, whereas Spaniards are more future-focused. Two groups of participants ($N = 40$ Moroccan and $N=40$ Spanish) completed a temporal-focus questionnaire that contained questions about past-focused ("PAST") and future-focused ("FUTURE") topics. In response to each question, participants provided a rating on a 5-point Likert scale on which lower scores indicated less agreement and higher scores indicated greater agreement. The authors then performed a mixed-design ANOVA with agreement score as the dependent variable, group (Moroccan or Spanish, between-subjects) as the fixed-effects factor, and temporal focus (past or future, within-subjects) as the random effects factor. In addition, the authors performed unpaired two-sample t-tests to determine whether there was a significant difference between the two groups in agreement scores for PAST questions, and whether there was a significant difference in scores for FUTURE questions.

------

#### Target outcomes: 
> According to a mixed analysis of variance (ANOVA) with group (Spanish vs. Moroccan) as a between-subjects factor and temporal focus (past vs. future) as a within-subjectS factor, temporal focus differed significantly between Spaniards and Moroccans, as indicated by a significant interaction of temporal focus and group, F(1, 78) = 19.12, p = .001, ηp2 = .20 (Fig. 2). Moroccans showed greater agreement with past-focused statements than Spaniards did, t(78) = 4.04, p = .001, and Spaniards showed greater agreement with future-focused statements than Moroccans did, t(78) = −3.32, p = .001. (de la Fuente et al., 2014, p. 1685).

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CARPSreports) # custom report functions
library(afex) # anova functions
library(ez)
```

```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared.
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

## Step 2: Load data

```{r}
data_path = 'data/DeLaFuenteEtAl_2014_RawData.xls'
d <- read_excel(data_path, sheet=3)
```

## Step 3: Tidy data

```{r}
# rename agreement
colnames(d)[5] <- 'agreement'

# change variable formats 
d$group <- factor(d$group)
d$participant <- d$participant
d$subscale <- factor(d$subscale) # "subscale" is the temporal focus
d$item <- factor(d$item)
d$agreement <- as.integer(d$agreement)

#rename participants so that identifiers are distinct in the two groups
moroccan_ids = d$participant[d$group=='Moroccan']
d$participant[d$group=='young Spaniard'] = d$participant[d$group=='young Spaniard'] + tail(moroccan_ids, 1)
d$participant <- factor(d$participant)

# view
head(d)
```

## Step 4: Run analysis

### Pre-processing

```{r}
# aggregate the data at the participant level
#   - collapse agreement scores for items within each level of subscale into a single (mean) value
d_agg <- d %>% 
  group_by(group, participant, subscale) %>% 
  summarise(agreement_score = mean(agreement))
```

### Descriptive statistics

```{r}
# None reported in the target outcome.
```

### Inferential statistics

>According to a mixed analysis of variance (ANOVA) with group (Spanish vs. Moroccan) as a between-subjects factor and temporal focus (past vs. future) as a within-subjects factor, temporal focus differed significantly between Spaniards and Moroccans, as indicated by a significant interaction of temporal focus and group, F(1, 78) = 19.12, p = .001, ηp2 = .20 (Fig. 2). Moroccans showed greater agreement with past-focused statements than Spaniards did, t(78) = 4.04, p = .001, and Spaniards showed greater agreement with future-focused statements than Moroccans did, t(78) = −3.32, p = .001.(de la Fuente et al., 2014, p. 1685)

```{r}
# ANALYSIS 1: Mixed-design ANOVA with group as between-subjects variable (fixed effect) and subscale as within-subjects variable (random effect), with partial eta-squared's
aov_group_subscale <- aov_car(agreement_score ~ group*subscale + Error(participant/subscale), data=d_agg, anova_table=list(es="pes"))
summary(aov_group_subscale) # detailed print-out
print(aov_group_subscale) # truncated output but includes partial eta-squared's

df_group_subscale <- aov_group_subscale$anova_table$`den Df`[3]
F_group_subscale <- aov_group_subscale$anova_table$F[3]
p_group_subscale <- aov_group_subscale$anova_table$`Pr(>F)`[3]
pes_group_subscale <- aov_group_subscale$anova_table$pes[3]

reportObject <- reproCheck(reportedValue = "78", obtainedValue = df_group_subscale, valueType = 'df')
reportObject <- reproCheck(reportedValue = "19.12", obtainedValue = F_group_subscale, valueType = 'F') # group:subscale F
reportObject <- reproCheck(reportedValue = ".001", obtainedValue = p_group_subscale, valueType = 'p') # group:subscale p
reportObject <- reproCheck(reportedValue = ".20", obtainedValue = pes_group_subscale, valueType = 'pes') # partial eta-squared

# ANALYSIS 2: Unpaired two-sample t-tests
# The authors don't specify whether they used one- or two-tailed tests, or which test (Student's t-test or Welch's), so I've done all four possible tests. However, I use the two-tailed Student's test as my obtained result for the purposes of comparison.

# TEST A: Are scores of the two groups significantly different for subscale=PAST?
moroccan_past <- d_agg %>% filter(subscale=='PAST', group=='Moroccan')
spanish_past <- d_agg %>% filter(subscale=='PAST', group=='young Spaniard')

t.test(moroccan_past$agreement_score, spanish_past$agreement_score, paired=FALSE, var.equal=TRUE, alternative=c("greater")) # one-tailed Student's
t.test(moroccan_past$agreement_score, spanish_past$agreement_score, paired=FALSE, var.equal=FALSE, alternative=c("greater")) # one-tailed Welch's
t_past <- t.test(moroccan_past$agreement_score, spanish_past$agreement_score, paired=FALSE, var.equal=TRUE) # two-tailed Student's 
t.test(moroccan_past$agreement_score, spanish_past$agreement_score, paired=FALSE, var.equal=FALSE) # two-tailed Welch's

df_ttest_past <- unname(t_past$parameter)
t_ttest_past <- unname(t_past$statistic)
p_ttest_past <- unname(t_past$p.value)

# compare reported with two-tailed Student's result
reportObject <- reproCheck(reportedValue = "78", obtainedValue = df_ttest_past, valueType = 'df') # df
reportObject <- reproCheck(reportedValue = "4.04", obtainedValue = t_ttest_past, valueType = 't') # t-statistic
reportObject <- reproCheck(reportedValue = ".001", obtainedValue = p_ttest_past, valueType = 'p') # p

# TEST B: Are scores of the two groups significantly different for subscale=FUTURE?
moroccan_future <- d_agg %>% filter(subscale=='FUTURE', group=='Moroccan')
spanish_future <- d_agg %>% filter(subscale=='FUTURE', group=='young Spaniard')

t.test(moroccan_future$agreement_score, spanish_future$agreement_score, paired=FALSE, var.equal=TRUE, alternative=c("less")) # one-tailed Student's
t.test(moroccan_future$agreement_score, spanish_future$agreement_score, paired=FALSE, var.equal=FALSE, alternative=c("less")) # one-tailed Welch's
t_future <- t.test(moroccan_future$agreement_score, spanish_future$agreement_score, paired=FALSE, var.equal=TRUE) # two-tailed Student's 
t.test(moroccan_future$agreement_score, spanish_future$agreement_score, paired=FALSE, var.equal=FALSE) # two-tailed Welch's

df_ttest_future <- unname(t_future$parameter)
t_ttest_future <- unname(t_future$statistic)
p_ttest_future <- unname(t_future$p.value)

# compare reported with two-tailed Student's result
reportObject <- reproCheck(reportedValue = "78", obtainedValue = df_ttest_future, valueType = 'df') # df
reportObject <- reproCheck(reportedValue = "-3.32", obtainedValue = t_ttest_future, valueType = 't') # t-statistic
reportObject <- reproCheck(reportedValue = ".001", obtainedValue = p_ttest_future, valueType = 'p') # p
```

## Step 5: Conclusion

This reproducability check was a failure.

The authors report that, on the mixed-design ANOVA, there is a significant interaction of temporal focus and group, with F(1, 78) = 19.12, p = .001, $\eta_{p}^{2}$ = .20. In our replication, we noted that two participants (25 and 65) had missing data for at least one level of the temporal focus variable (de la Fuente et al. make no mention of any excluded participants in their methods), and our ANOVA function automatically removed these participants. We suspect this may be the reason that our obtained degrees of freedom differed from those reported by the authors. In addition to a difference in df (minor numerical error), we observed a difference in F-statistic (minor) and p value (major).

Similarly, there was a difference in obtained versus reported degrees of freedom (minor), t-statistic (minor), and p value (major) on the t-test for the Past subscale, and in obtained versus reported t-statistic (minor), and p value (major) on the t-test for the Future subscale. We do not have any hypotheses about the cause of the difference in t-statistics or degrees of freedom. One possibility is that the p values were off because the authors reported that p = .001 when they meant to report that p < .001.

```{r}
Author_Assistance = FALSE # was author assistance provided? (if so, enter TRUE)

Insufficient_Information_Errors <- 0 # how many discrete insufficient information issues did you encounter?

# Assess the causal locus (discrete reproducibility issues) of any reproducibility errors. Note that there doesn't necessarily have to be a one-to-one correspondance between discrete reproducibility issues and reproducibility errors. For example, it could be that the original article neglects to mention that a Greenhouse-Geisser correct was applied to ANOVA outcomes. This might result in multiple reproducibility errors, but there is a single causal locus (discrete reproducibility issue).

locus_typo <- NA # how many discrete issues did you encounter that related to typographical errors?
locus_specification <- NA # how many discrete issues did you encounter that related to incomplete, incorrect, or unclear specification of the original analyses?
locus_analysis <- NA # how many discrete issues did you encounter that related to errors in the authors' original analyses?
locus_data <- NA # how many discrete issues did you encounter that related to errors in the data files shared by the authors?
locus_unidentified <- NA # how many discrete issues were there for which you could not identify the cause

Affects_Conclusion <- FALSE # Do any reproducibility issues encounter appear to affect the conclusions made in the original article? This is a subjective judgement, but you should taking into account multiple factors, such as the presence/absence of decision errors, the number of target outcomes that could not be reproduced, the type of outcomes that could or could not be reproduced, the difference in magnitude of effect sizes, and the predictions of the specific hypothesis under scrutiny.
```

```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add the articleID 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome != "MATCH") | Insufficient_Information_Errors > 0){
  finalOutcome <- "Failure without author assistance"
  if(Author_Assistance == T){
    finalOutcome <- "Failure despite author assistance"
  }
}else{
  finalOutcome <- "Success without author assistance"
  if(Author_Assistance == T){
    finalOutcome <- "Success with author assistance"
  }
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, Author_Assistance, finalOutcome, Insufficient_Information_Errors, locus_typo, locus_specification, locus_analysis, locus_data, locus_unidentified)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "final"){
  write_csv(reportObject, "finalReportDetailed.csv")
  write_csv(reportExtras, "finalReportExtras.csv")
}
```

# Session information

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
