---
title: "CARPS Reproducibility Report"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

#### Article ID: CARPS_3-9-2014_PS
#### Pilot 1: Katherine Hermann
#### Co-pilot: Benjamin deMayo
#### Start date: 11/4/2017
#### End date: 11/7/2017   

-------

#### Methods summary: 
This analysis pertains to Experiment 2 of de la Fuente et al. (2014). In that experiment, the researchers tested the question of whether temporal focus differs between Moroccan and Spanish cultures, hypothesizing that Moroccans are more past-focused, whereas Spaniards are more future-focused. Two groups of participants ($N = 40$ Moroccan and $N=40$ Spanish) completed a temporal-focus questionnaire that contained questions about past-focused ("PAST") and future-focused ("FUTURE") topics. In response to each question, participants provided a rating on a 5-point Likert scale on which lower scores indicated less agreement and higher scores indicated greater agreement. The authors then performed a mixed-design ANOVA with agreement score as the dependent variable, group (Moroccan or Spanish, between-subjects) as the fixed-effects factor, and temporal focus (past or future, within-subjects) as the random effects factor. In addition, the authors performed unpaired two-sample t-tests to determine whether there was a significant difference between the two groups in agreement scores for PAST questions, and whether there was a significant difference in scores for FUTURE questions.

------

#### Target outcomes: 
"According to a mixed analysis of variance (ANOVA) with
group (Spanish vs. Moroccan) as a between-subjects factor and temporal focus (past vs. future) as a within-subjects factor, temporal focus differed significantly between
Spaniards and Moroccans, as indicated by a significant
interaction of temporal focus and group, F(1, 78) = 19.12,
p = .001, $\eta_{p}^{2}$ = .20 (Fig. 2). Moroccans showed greater
agreement with past-focused statements than Spaniards
did, t(78) = 4.04, p = .001, and Spaniards showed greater
agreement with future-focused statements than Moroccans
did, t(78) = -3.32, p = .001" (de la Fuente et al., 2014).

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CARPSreports) # custom report functions
library(afex) # anova functions
```

## Step 2: Load data

```{r}
data_path = 'data/DeLaFuenteEtAl_2014_RawData.xls'
d <- read_excel(data_path, sheet=3)
```

## Step 3: Tidy data

```{r}
# rename agreement
colnames(d)[5] <- 'agreement'

# change variable formats 
d$group <- factor(d$group)
d$participant <- d$participant
d$subscale <- factor(d$subscale) # "subscale" is the temporal focus
d$item <- factor(d$item)
d$agreement <- as.integer(d$agreement)

#rename participants so that identifiers are distinct in the two groups
moroccan_ids = d$participant[d$group=='Moroccan']
d$participant[d$group=='young Spaniard'] = d$participant[d$group=='young Spaniard'] + tail(moroccan_ids, 1)
d$participant <- factor(d$participant)

# view
head(d)
```

## Step 4: Run analysis

### Pre-processing

```{r}
# aggregate the data at the participant level
#   - collapse agreement scores for items within each level of subscale into a single (mean) value
d_agg <- d %>% 
  group_by(group, participant, subscale) %>% 
  summarise(agreement_score = mean(agreement))
```

### Descriptive statistics

```{r}
# None reported in the target outcome.
```

### Inferential statistics

```{r}
# ANALYSIS 1: Mixed-design ANOVA with group as between-subjects variable (fixed effect) and subscale as within-subjects variable (mixed effect), with partial eta-squared's
aov_group_subscale <- aov_car(agreement_score ~ group*subscale + Error(participant/subscale), data=d_agg, anova_table=list(es="pes"))
summary(aov_group_subscale) # detailed print-out
print(aov_group_subscale) # truncated output but includes partial eta-squared's

compareValues(reportedValue = 78, obtainedValue = 76) # df
compareValues(reportedValue = 19.12, obtainedValue = 18.3456) # group:subscale F
compareValues(reportedValue = .001, obtainedValue = 0.00005328, isP = T) # group:subscale p
compareValues(reportedValue = .20, obtainedValue = .19) # partial eta-squared
# NOTE: why does compareValues return MATCH for the partial eta-squareds?

# ANALYSIS 2: Unpaired two-sample t-tests
# The authors don't specify whether they used one- or two-tailed tests, or which test (Student's t-test or Welch's), so I've done all four possible tests. However, I use the two-tailed Student's test as my obtained result for the purposes of comparison.

# TEST A: Are scores of the two groups significantly different for subscale=PAST?
moroccan_past <- d_agg %>% filter(subscale=='PAST', group=='Moroccan')
spanish_past <- d_agg %>% filter(subscale=='PAST', group=='young Spaniard')

t.test(moroccan_past$agreement_score, spanish_past$agreement_score, paired=FALSE, var.equal=TRUE, alternative=c("greater")) # one-tailed Student's
t.test(moroccan_past$agreement_score, spanish_past$agreement_score, paired=FALSE, var.equal=FALSE, alternative=c("greater")) # one-tailed Welch's
t.test(moroccan_past$agreement_score, spanish_past$agreement_score, paired=FALSE, var.equal=TRUE) # two-tailed Student's 
t.test(moroccan_past$agreement_score, spanish_past$agreement_score, paired=FALSE, var.equal=FALSE) # two-tailed Welch's

# compare reported with two-tailed Student's result
compareValues(reportedValue = 78, obtainedValue = 76) # df
compareValues(reportedValue = 4.04, obtainedValue = 3.8562) # t-statistic
compareValues(reportedValue = .001, obtainedValue = .0002394, isP = T) # p

# TEST B: Are scores of the two groups significantly different for subscale=FUTURE?
moroccan_future <- d_agg %>% filter(subscale=='FUTURE', group=='Moroccan')
spanish_future <- d_agg %>% filter(subscale=='FUTURE', group=='young Spaniard')

t.test(moroccan_future$agreement_score, spanish_future$agreement_score, paired=FALSE, var.equal=TRUE, alternative=c("less")) # one-tailed Student's
t.test(moroccan_future$agreement_score, spanish_future$agreement_score, paired=FALSE, var.equal=FALSE, alternative=c("less")) # one-tailed Welch's
t.test(moroccan_future$agreement_score, spanish_future$agreement_score, paired=FALSE, var.equal=TRUE) # two-tailed Student's 
t.test(moroccan_future$agreement_score, spanish_future$agreement_score, paired=FALSE, var.equal=FALSE) # two-tailed Welch's

# compare reported with two-tailed Student's result
compareValues(reportedValue = 78, obtainedValue = 76) # df
compareValues(reportedValue = -3.32, obtainedValue = -3.2098) # t-statistic
compareValues(reportedValue = .001, obtainedValue = .001929, isP = T) # p
```

## Step 5: Conclusion

```{r}
carpsReport(Report_Type = "pilot", 
            Article_ID = "CARPS_3-9-2014_PS", 
            Insufficient_Information_Errors = 0,
            Decision_Errors = 0,
            Major_Numerical_Errors = 3, 
            Time_to_Complete = 240, 
            Author_Assistance = FALSE)
```

This reproducability check was a failure: there were 3 major numerical errors and a number of minor numerical errors.

The authors report that, on the mixed-design ANOVA, there is a significant interaction of temporal focus and group, with F(1, 78) = 19.12, p = .001, $\eta_{p}^{2}$ = .20. In our replication, we noted that two participants (25 and 65) had missing data for at least one level of the temporal focus variable (de la Fuente et al. make no mention of any excluded participants in their methods), and our ANOVA function automatically removed these participants. We suspect this may be the reason that our obtained degrees of freedom differed from those reported by the authors. In addition to a difference in df (minor numerical error), we observed a difference in F-statistic (minor) and p value (major).

Similarly, there was a difference in obtained versus reported degrees of freedom (minor), t-statistic (minor), and p value (major) on the both t-tests. We do not have any hypotheses about the cause of the difference.

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
